---
title: '**Assignment 2: Web scrapping/Data Wrangling in R**'
author: '**Suman Paudel 33**'
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
  pdf_document: 
    highlight: pygments
---

[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

### [ <b> Code Execution and Output/Interpretation of Session 7</b>]{style="color:#d30000"}

#### What is a “package” in R?

-   In R, the fundamental unit of shareable code/function is the package.
-   A package bundles together code, data, documentation, and tests, and is easy to share with others.
-   The public clearing house for R packages is the Comprehensive R Archive Network or `CRAN`. The details about the packages can be found at CRAN.

#### How to install, use and get help about any package from CRAN?

-   We can install packages of CRAN in R using: **`install.packages("packagename")`**\
    For example: **`install.packages("dplyr")`**

-   We can then use the installed packages in R using:\
    **`library(packagename)`**\
    **`e.g. library(dplyr)`**

-   We can get help on the installed packages in R using:\
    **`?packagement`** or **`help(package = "packagement")`**\
    **`e.g. ?dplyr`** OR **`help(package = "dplyr")`**

#### How to develop a package in R?  

\ <https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/>

-   Step 0: Packages you will need
-   Step 1: Creating your package directory
-   Step 2: Add functions
-   Step 3: Add documentation
-   Step 4: Process your documentation
-   Step 5: Install
-   Step 6: Make a package GitHub repo (Bonus!)
-   Step 7: Infinity- Iterate

#### Reading (Import) data in R/R Studio:

-   Text files: R base, readr etc
-   Excel files: readXL, openxls etc.
-   SPSS, Stata, SAS files: foreign, haven etc.

#### Reading data in R/R Studio

-   JSON files: rjason, jsonlite, RJSONIO etc.

#### To install the library to work on josn files.
-   `install.packages('jsonlite')`
-   `install.packages('rjson')`

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# vector 
library("rjson")
data <- fromJSON(file = "jason_data.json")
data
```

***Interpretation***:

-   loaded the jason_data.json file fromm current working directory using rjson library

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
library("rjson")
data <- fromJSON(file = "jason_data.json")
data
```

***Interpretation***:

-   loaded the jason_data.json file fromm current working directory using rjson library

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# covert to data frame:
jason_data_frame <- as.data.frame(data)
jason_data_frame
```

***Interpretation***:

-   converted the loaded json data into data.frame

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# summary of jason_data_frame
summary(jason_data_frame)
```

***Interpretation***:

-   summarizes the json data frame.

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# average salary by department
aggregate(Salary ~ Dept, data = jason_data_frame, FUN = mean)
```

***Interpretation***:

- aggregates the average salary by department.

```{r}
# also using dplyr package
library(dplyr)
library(magrittr)
avg_by_dept <-
  jason_data_frame %>%
  group_by(Dept) %>%
  summarise(avg_salart = mean(Salary))
```

***Interpretation***:

- average salary by department can be achieved by using dplyr package and using summarise.

```{r}
# frequency distribution of all variables
# since tables only shows the frequency distribution of factors, table on numerical or integer value is bad practice.
table(jason_data_frame$Dept)
```

***Interpretation***:

- since tables only shows the frequency distribution of factors, table on numerical or integer value is bad practice.


#### Reading JSON file from URL: Web API 

```{r cache=TRUE}
# fetch the data from web api
library(jsonlite)
raw <-
  fromJSON(
    "https://data.ny.gov/api/views/9a8c-vfzj/rows.json?accessType=DOWNLOAD")
food_market <- raw[['data']] 
```

***Interpretation***:

- read the json data from API using jsonlite library
- the raw object gets the list of values from where data part is extracted and assigned to food_market object

```{r}
# structure and head of food market
str(food_market) 
head(food_market, n = 4)
```

***Interpretation***:

- returns the structure and head of food_market.

```{r}
names <- food_market[,14]
```

***Interpretation***:

- returns the names stores listed in index 14 of food_market in names object

```{r}
head(names)
head(table(names), n = 7)
```

***Interpretation***:

- `head(names)` returns first few data.
- `head(table(names), n = 7)` returns the frequency table of names of stores.
- since data is so much I restricted to first 7 values for frequency table.

```{r error=TRUE}
table(v19)
```

***Interpretation***:

- trying to get the frequency tabke v19. but v19 doesn't exist and throws error

```{r error=TRUE}
table(food_market$V19)
```

***Interpretation***:

- An atomic vector is a one-dimensional data object created using functions like c() or vector() in R.
- The $ operator is commonly used to access elements of a data frame by column name.
- since food_market is of atomic vectors type, while access the element using $ returned this error.
- this can be mitigated by using `table(food_market[,19])`

```{r, warning=FALSE}
head(table(food_market[, 19]), n = 5)
```

***Interpretation***:

- returns the frequency table of data that is at 19th column of food_market
- since data is too much, I restricted the display to 5.

#### Web scrapping in R: A Simple (barebones) Example

```{r warning=FALSE}
# The recommended package for web scrapping in R is “rvest
# using html
library(rvest)
simple <-
  read_html('https://dataquestio.github.io/web-scraping-pages/simple.html')
simple %>% html_nodes('p') %>% html_text()
```

***Interpretation***:

- reads the html using `read_html()`
- we loaded the html in simple object then using pipes parsed the html with node 'p' then converted that to normal text.

```{r}
# Wikipedia Nepal Covid 19 
wiki_link <- "https://en.wikipedia.org/wiki/COVID-19_pandemic_in_Nepal"
wiki_page <- read_html(wiki_link)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
str(wiki_page)
```

***Interpretation***:

- structure of wiki page, returns list of 2 xml node and xml doc

```{r}
wiki_page %>% html_nodes("table")
```

***Interpretation***:

- parses the html nodes containing `table` in html page of wiki_page.

```{r}
covid_table <-
  wiki_page %>% html_elements('.COVID-19_pandemic_data_Nepal_medical_cases') %>% html_node('table') %>% html_table()
covid_table <- covid_table[[1]]
```

***Interpretation***:

- from wiki page, first parsed the html elements having `.COVID-19_pandemic_data_Nepal_medical_cases`
- then extracted the node containing `table` into html_table()
- since the data was returned in the list, the actual data was at first index which is dataframe.


#### Data wrangling: Part I Column names of covid_table
```{r}
names(covid_table) <-
  paste(names(covid_table), covid_table[1, ], sep = "_")
covid_table <- covid_table[-1, ]
names(covid_table)
```

***Interpretation***:

- even though the data was extracted to dataframe there was error in columns and we want to rename it
- concatenated the column names with first row of dataframe.
- and finally dropping the first column.


```{r}
#Check the structure of data again
str(covid_table)
```

***Interpretation***:

- checking the structure again to ensure.

#### Data wrangling: Part II Renaming the column names
- Change “Date_Date” variable as “Date”
- Change “Confirmed cases_Total” variable as “Confirmed_Cases_Total”
- Change “Confirmed cases_New” variable as “Confirmed_Cases_New”
- Change “Confirmed cases_Active” variable as “Confirmed_Cases_Active”
- Change “RT-PCR tests_Total” variable as “RT-PCR_tests_Total”
- Change “RT-PCR tests_New” variable as “RT-PCR_tests_New”
- Change “TPR_TPR” variable as “TPR”
- Change “RR_RR” variable as “RR”
- Change “CFR_CFR” variable as “CFR”
- Change “Ref. _Ref.” variable as “Ref”


```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.


```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r eval=FALSE}
# another way to do same thing 

names(covid_table)[names(covid_table)=='Date_Date'] = 'Date'
names(covid_table)[names(covid_table)=='Confirmed cases_Total'] = 'Confirmed_Cases_Total'
names(covid_table)[names(covid_table)=='Confirmed cases_New'] = 'Confirmed_Cases_New'
names(covid_table)[names(covid_table)=='Confirmed cases_Active'] = 'Confirmed_Cases_Active'
names(covid_table)[names(covid_table)=='Recoveries_Total'] = 'Recoveries_Total'
names(covid_table)[names(covid_table)=='Recoveries_New'] = 'Recoveries_New'
names(covid_table)[names(covid_table)=='Deaths_Total'] = 'Deaths_Total'
names(covid_table)[names(covid_table)=='Deaths_New'] = 'Deaths_New'
names(covid_table)[names(covid_table)=='RT-PCR tests_Total'] = 'PCR_Total'
names(covid_table)[names(covid_table)=='RT-PCR tests_New'] = 'PCR_New'
names(covid_table)[names(covid_table)=='TPR_TPR'] = 'TPR'
names(covid_table)[names(covid_table)=='RR_RR'] = 'RR'
names(covid_table)[names(covid_table)=='CFR_CFR'] = 'CFR'
names(covid_table)[names(covid_table)=='Ref._Ref.'] = 'Ref'
```

***Interpretation***:

- Another way to rename the column names to desired column names.

#### Data Wrangling Part III
```{r}

# removing "+" and "%" from the variables
covid_table$Confirmed_Cases_New <- gsub('[+]', '', covid_table$Confirmed_Cases_New)
covid_table$Recoveries_New <- gsub('[+]', '', covid_table$Recoveries_New)
covid_table$Deaths_New <- gsub('[+]', '', covid_table$Deaths_New)
covid_table$PCR_New <- gsub('[+]', '', covid_table$PCR_New)

covid_table$TPR <- gsub('[%]', '', covid_table$TPR)
covid_table$RR <- gsub('[%]', '', covid_table$RR)
covid_table$CFR <- gsub('[%]', '', covid_table$CFR)

```

***Interpretation***:

- cleaning the messy data using gsub.
- removing `%` and `+` from data.

```{r}
# since in pdf while converting chr to numeric or integer type coerce warning was given for invalid type.
covid_table$Confirmed_Cases_Total <- gsub('[,]', '', covid_table$Confirmed_Cases_Total)
covid_table$Confirmed_Cases_New <- gsub('[,]', '', covid_table$Confirmed_Cases_New)
covid_table$Confirmed_Cases_Active <- gsub('[,]', '', covid_table$Confirmed_Cases_Active)
covid_table$Recoveries_Total <- gsub('[,]', '', covid_table$Recoveries_Total)
covid_table$Recoveries_New <- gsub('[,]', '', covid_table$Recoveries_New)

covid_table$Deaths_Total <- gsub('[,]', '', covid_table$Deaths_Total)
covid_table$Deaths_New <- gsub('[,]', '', covid_table$Deaths_New)
covid_table$PCR_Total <- gsub('[,]', '', covid_table$PCR_Total)
covid_table$PCR_New <- gsub('[,]', '', covid_table$PCR_New)

covid_table$TPR <- gsub('[,]', '', covid_table$TPR)
covid_table$RR <- gsub('[,]', '', covid_table$RR)
covid_table$CFR <- gsub('[,]', '', covid_table$CFR)
```

***Interpretation***:

- Since while converting chr to integer type it gave some warning about coerce where values were invalid type for e.g `313,333` can't be interpreted as integer because of comma. But it is right in context of html in website. 
- removed the `,` using gsub.

#### Data wrangling: Part IV Converting “chr” variables as numbers 

```{r}

covid_table$Confirmed_Cases_Total <-
  as.integer(covid_table$Confirmed_Cases_Total)
covid_table$Confirmed_Cases_New <-
  as.integer(covid_table$Confirmed_Cases_New)
covid_table$Confirmed_Cases_Active <-
  as.integer(covid_table$Confirmed_Cases_Active)
covid_table$Recoveries_Total <-
  as.integer(covid_table$Recoveries_Total)
covid_table$Recoveries_New <-
  as.integer(covid_table$Recoveries_New)

covid_table$Deaths_Total <- as.integer(covid_table$Deaths_Total)
covid_table$Deaths_New <- as.integer(covid_table$Deaths_New)
covid_table$PCR_Total <- as.integer(covid_table$PCR_Total)
covid_table$PCR_New <- as.integer(covid_table$PCR_New)

covid_table$TPR <- as.numeric(covid_table$TPR)
covid_table$RR <- as.numeric(covid_table$RR)
covid_table$CFR <- as.numeric(covid_table$CFR)
```

***Interpretation***:

- converted all of the required columns of chr type of integer or numeric type using `as.numeric()` function.

```{r}
str(covid_table)
```

***Interpretation***:

- finally check the data type.


##### Converting Date (Assignment)
```{r}
head(as.Date(covid_table$Date, format = "%d %b"), n = 50)
```

***Interpretation***:

- By default tries to check this format `"%Y-%m-%d"` or `"%Y/%m/%d"`for given date or string data.
- since out date column has day and month I have to use `%d` for day and `%b` for short name of month.
- returns the value in 2024 but that date is of 2020 and 2021
- In order to work around this I have made a logic below.

```{r }
# using base R date time functions

start_date_2020 <- "2020-01-23"
end_date_2020 <- "2020-12-31"

# check days diff
days_diff <-
  as.numeric(difftime(end_date_2020, start_date_2020, units = 'days')) + 1

# check difference till first n rows and insert value if condition is true return 2020 else 2021
check_year <- ifelse(1:nrow(covid_table) <= days_diff, 2020, 2021)

# format the date according to need
formatted_date <- as.Date(covid_table$Date, format = "%d %b")
formatted_date <- format(formatted_date, '-%m-%d')

# concantante the year and formated day and date
final_converted_date <- paste0(check_year, formatted_date)

# finally since concatenation returns string again convert the type into date and load the Date column of covid table
covid_table$Date <- as.Date(final_converted_date)
head(covid_table$Date)
class(covid_table$Date)
```

***Interpretation***:

- Since I know that data is of 23rd Jan 2020 to 31st May 2021.
- Also, after 31st Dec next year will arrive, so I set variable `start_date_2020 <- "2020-01-23"` and `end_date_2020 <- "2020-12-31"`.
- I calculated the difference in day from 23rd Jan to 31st Dec.
- Also data is serial in dataframe I filtered the data to 2020 and 2021 using difference in rows. Set `2020` to first 344 rows and rest `2021`.
- since `as.Date(covid_table$Date, format = "%d %b")` gave the date of 2024, I formatted the date and only got day and month.
- Finally concatenated the calulcated year with formatted day and month. 

```{r, warning=FALSE, message=FALSE}
# using lubridate
library(lubridate)

start_date_2020 <- "2020-01-23"
end_date_2020 <- "2020-12-31"

# find difference
diff <-
  (ymd(start_date_2020) %--% ymd(end_date_2020)) %/% days(1) + 1

# check difference till first n rows and insert value if condition is true return 2020 else 2021
check_year <- ifelse(1:nrow(covid_table) <= diff, 2020, 2021)

# format the date to day and month 
formatted_date <- ymd(as.Date(covid_table$Date, format = "%d %b"))

# create the date using make_date function
final_converted_date <-
  make_date(
    year = check_year,
    month = month(formatted_date),
    day = day(formatted_date)
  )
# change the Date column value with final converted date 
covid_table$Date <- final_converted_date
class(covid_table$Date)
```

***Interpretation***:

- Using lubridate to achieve the solution to given problem.



### [ <b> Code Execution and Output/Interpretation of Session 7</b>]{style="color:#d30000"}

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
```

```{r}
table1 <- tibble(
  country = c("Afghanistan", "Afghanistan", "Brazil", 
               "Brazil", "China", "China"),
  year = c(1999, 2000, 1999, 2000, 1999, 2000),
  cases = c(745,2666,37737,80488,212258,213766),
  population = c(19987071,20595360,172006362, 
                 174504898, 1272915272,1280428583)
)

table1
table2
table3
table4a
table4b
```

***Interpretation***:

- Exploring the few built in tables from tidyverse package.
- There are two main advantages:
  - There’s a general advantage to picking one consistent way of storing 
data. If you have a consistent data structure, it’s easier to learn the 
tools that work with it because they have an underlying uniformity.
  - There’s a specific advantage to placing variables in columns because it 
allows R’s vectorized nature to shine.
  - dplyr, ggplot2, and all the other packages in the tidyverse are 
designed to work with tidy data.


```{r}
# Pivoting – Longer to wider
# (To do standard statistical analysis)
table2 %>% pivot_wider(names_from = type, values_from = count)
```

***Interpretation***:

- Pivoting the `table2` from longer to wider.
- usually used for standard statistical analysis

```{r}
# Pivoting – Wider to Longer
# (To do Variance components analysis)
table4a %>%
  pivot_longer(c(`1999`, `2000`), names_to =
                 "year", values_to = "cases")
```

***Interpretation***:

- Pivoting the `table2` from  wider to longer.
- usually used for standard statistical analysis.

```{r}
# Tidy data: Separate
table3 %>% separate(rate, into = c("cases", "population"))
# OR
table3 %>% separate(rate, into = c("cases", "population"), sep = "/")
```

***Interpretation***:

- separate the value from single column to multiple columns.
- often useful when dealing with delimited values in single column.

```{r}
# Tidy data: Unite
table5 %>% unite(new, century, year)
# OR
table5 %>% unite(new, century, year, sep = "")
```

***Interpretation***:

- unites columns into one.
- opposite of separate: it combines multiple columns into a single column.
- 
```{r}
# Missing values: Example
stocks <- tibble(
  year = c(2015, 2015, 2015, 2015, 2016, 2016, 2016),
  qtr = c( 1, 2, 3, 4, 2, 3, 4),
  return = c(1.88, 0.59, 0.35, NA, 0.92, 0.17, 2.66)
)

stocks %>% pivot_wider(names_from = year, values_from = return)
```

***Interpretation***:

- pivoted the stocks to wider to check missing values on year and return
- The return for the fourth quarter of 2015 is explicitly missing, 
because the cell where its value should be instead contains NA.
- The return for the first quarter of 2016 is implicitly missing, because it simply does not appear in the dataset.


```{r}
stocks %>%
  pivot_wider(names_from = year, values_from = return) %>%
  pivot_longer(
    cols = c(`2015`, `2016`),
    names_to = "year",
    values_to = "return",
    values_drop_na = TRUE
  )
```

***Interpretation***:

- `pivot_wider(names_from = year, values_from = return)` pivots data from longer to wider format. the date is spread out based on different years, where year is the column providing the year information, and return is the column providing return values.
- `pivot_longer()` is used to pivot data from wider to longer format. It gathers columns specified in cols into key-value pairs. Here, it specifies to gather columns 2015 and 2016 into a new column named "year", with their corresponding values into a new column named "return". The parameter values_drop_na = TRUE indicates that rows with missing values after pivoting should be dropped.

```{r}
stocks %>% complete(year, qtr)
```

***Interpretation***:

- `complete()` is used to complete a data frame with missing combinations of values. It takes columns specified in the arguments and ensures that all combinations of unique values are present in the resulting data frame. 
- here, it ensures that all combinations of values from the columns year and qtr are present in the data frame, filling in any missing combinations with NA values.

```{r}
treatment <- tribble(
~ person, ~ treatment, ~response,
"Derrick Whitmore", 1, 7,
NA, 2, 10,
NA, 3, 9,
"Katherine Burke", 1, 4
)
treatment

```

***Interpretation***:

- Create tibbles using an easier to read row-by-row layout. This is useful for small tables of data where readability is important.

```{r}
treatment %>% fill(person)
```

***Interpretation***:

- `fill(person)` fills missing values in the specified column (person in this case) with the most recent non-missing value in that column.


#### Transform/manipulate data with “dplyr”

###### To learn five key “dplyr” package functions that allow you to solve the vast majority of your data manipulation challenges:
- **``filter())``** function is used to subset a data frame, retaining all rows that satisfy your conditions.
- **``(arrange()``**: orders the rows of a data frame by the values of selected columns.
- **``select()``**: (and optionally rename) variables in a data frame, using a concise mini-language that makes it easy to refer to variables based on their name (e.g. a:f selects all columns from a on the left to f on the right) or type (e.g. where(is.numeric) selects all numeric columns).
- **``mutate()``**: creates new columns that are functions of existing variables. It can also modify (if the name is the same as an existing column) and delete columns (by setting their value to NULL). Collapse many values down to a single summary 
- **``summarise()``**: It returns one row for each combination of grouping variables; if there are no grouping variables, the output will have a single row summarizing all observations in the input. It will contain one column for each grouping variable and one column for each of the summary statistics that you have specified
- **``group_by()``**: Most data operations are done on groups defined by variables. group_by() takes an existing tbl and converts it into a grouped tbl where operations are performed "by group". ungroup() removes grouping.


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(nycflights13)
flights
```

***Interpretation***:

- load the flights dataset.


###### Filter
```{r}
filter(flights, month == 1, day == 1)
```

***Interpretation***:

- filters flights datasets for all months and day equals to 1

```{r}

# filter jan1
jan1 <- filter(flights, month == 1, day == 1)
(jan1 <- filter(flights, month == 1, day == 1))

# filter dec25
dec25 <- filter(flights, day ==12 , day == 25)
(dec25 <- filter(flights, day ==12 , day == 25))
```

***Interpretation***:

- filters January 1 for all flights data.
- filters December 25 for all flights data.

```{r error=TRUE}
filter(flights, month = 1) #throws error
filter(flights, month == 1) #works fine
```

***Interpretation***:

- `filter(flights, month = 1)` will throw an error because month=1 doesn't filter but assigns the value 1 to month.
- filter(flights, month == 1) will filter the month 1.

```{r}

# valid filter to fetch only rows where the month is either November December.
filter(flights, month == 11 | month == 12)

# returns all row since 11 | 12 computes to TRUE
filter(flights, month == 11 | 12)

# valid filter to fetch only rows where the month is either November December.
nov_dec <- filter(flights, month %in% c(11, 12))
```

***Interpretation***:

- `filter(flights, month == 11 | month == 12)` fetch only rows where the month is either November December.
- `filter(flights, month == 11 | 12)` returns all row since 11 | 12 computes to TRUE, even though syntactically it returns values but it won't gives us desired output.
- `nov_dec <- filter(flights, month %in% c(11, 12))` fetch only rows where the month is either November December.


```{r}

# De Morgan's Law:
filter(flights, !(arr_delay > 120 | dep_delay > 120))
filter(flights, arr_delay <= 120, dep_delay <= 120) 
```

***Interpretation***:

- Both returns the same value: `filter(flights, !(arr_delay > 120 | dep_delay > 120))` filters all arrival and departure delayed which are not greater 120.
- `filter(flights, arr_delay <= 120, dep_delay <= 120)` filters all arrival and departure delayed which are less than or equal to 120.
- 

###### Arrange Example
```{r}

# by default sorts in ascending order
arrange(flights, year, month, day)

# descending order
arrange(flights, desc(dep_delay))
```

***Interpretation***:

- `arrange(flights, year, month, day)` sorts year, month and day in ascending order.  
- `arrange(flights, year, month, day)` sorts year, month and day in descending order. 
- Missing values are always sorted at the end.


##### Select Example

```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).

```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

flights %>% select(starts_with('d')) #matches names beginning with d
flights %>% select(ends_with('e')) #matches names ending with e
flights %>% select(contains('d')) #matches names containing with d
flights %>% select(matches("(.)\\1")) #matches any variables that contain repeated characters
flights %>% select(num_range("dest",1:15)) #matches if dest contains any range between 1 to 15
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).


```{r}

# Select columns by name
select(flights, year, month, day)
# Select all columns between year and day (inclusive)
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

***Interpretation***:

- `select(flights, year, month, day)` selects year, month and day from flights.
- `select(flights, year:day)` selects all columns between year and day (inclusive) from flights.
- `select(flights, year, month, day)` selects all columns except those from year to day (inclusive).

