---
title: '**Assignment 2: Web scrapping/Data Wrangling in R**'
author: '**Suman Paudel 33**'
date: "2024-03-03"
output:
  pdf_document: default
  github_document: default
  html_notebook: default
  html_document: default
---
[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

## <span style="color:#d30000"> <b> Code Execution and Output/Interpretation of Session 4</b></span>

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# vector 
x <- c(1:30)
y <- x^3
plot(x,y,)
```

***Interpretation***:

-   x is vector having elements 1 to 30. 
-   y is also vector having elements of x exponentiated of 3. 
-   plot is a generic function in R to plot, by default in R scatter plot is plotted.


##### <span style="color:#7b9a26"> <b> Code Sample 2</b></span>

```{r}
# store the current working using following command:
initial.dir <- getwd()
initial.dir
```

***Interpretation***:

-   **initial.dir** object will be assigned the current working directory.

##### <span style="color:#7b9a26"> <b> Code Sample 3</b></span>

```{r}
# to change the working directory custom directory
setwd("C:/Users/SumanPaudel/Desktop/R For Data Science")
```

***Interpretation***:

-   **setwd()** function will change the working directory to given path.

 