---
title: "**Project 1: Unit 1**"
author: "**Suman Paudel**"
date: "2024-02-26"
output:
  html_document: default
  pdf_document: default
---
[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

## <span style="color:#d30000"> <b> Code Execution and Output/Interpretation of Session 4</b></span>

\

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# vector 
x <- c(1:30)
y <- x^3
plot(x,y,)
```

***Interpretation***:

-   x is vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default in R scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 2</b></span>

```{r}
# store the current working using following command:
initial.dir <- getwd()
initial.dir
```

***Interpretation***:

-   **initial.dir** object will be assigned the current working directory.

\

##### <span style="color:#7b9a26"> <b> Code Sample 3</b></span>

```{r}
# to change the working directory custom directory
setwd("C:/Users/SumanPaudel/Desktop/R For Data Science")
```

***Interpretation***:

-   **setwd()** function will change the working directory to given path.

\

##### <span style="color:#7b9a26"> <b> Code Sample 4</b></span>

```{r}
# loading the necessary packages
library(magrittr)
```

***Interpretation***:

-   In R, the **library()** function will load and attach the required packages.

\

##### <span style="color:#7b9a26"> <b> Code Sample 5</b></span>

```{r eval=FALSE}
# to set the output file and bypass the output of R console and R Studio
sink('session4.out')
```

***Interpretation***:

-   In R, the **sink()** function will set the output file and bypass the output of R console and R Studio.
- until closed, now all the output will be saved in the session4.out file rather than display on.

\

##### <span style="color:#7b9a26"> <b> Code Sample 6</b></span>

```{r}
# load the dataset from the working directory set earlier
iris <- read.csv('iris.csv')
```

***Interpretation***:

- load the iris dataset from csv file using module **read.csv()** function.

\

##### <span style="color:#7b9a26"> <b> Code Sample 7</b></span>

```{r,eval=FALSE}
# plot the iris dataset to do some analysis
plot(iris)
```

***Interpretation***:

- plot a scatter plot from the iris dataset.
- since we have used **sink()** function earlier now the given output will be saved to session4.out

\

##### <span style="color:#7b9a26"> <b> Code Sample 8</b></span>

```{r,eval=FALSE}
# summary of iris dataset
summary(iris)
```

***Interpretation***:

- In R, **summary** summary is a generic function used to produce result summaries of the results of various model fitting functions.
- since we have used **sink()** function earlier now the given output will be saved to session4.out

\

##### <span style="color:#7b9a26"> <b> Code Sample 9</b></span>

```{r}
# to close the output file
sink()
```

***Interpretation***:

- Closes the output file that was writing output to it.

\

##### <span style="color:#7b9a26"> <b> Code Sample 10</b></span>

```{r}
# unloading the loaded library
detach("package:magrittr")
```

***Interpretation***:

- Unloads the previous loaded package **magrittr**. 
- Usually use to unload or remove the path of R objects, packages which was attached by using **library()**.

\

##### <span style="color:#7b9a26"> <b> Code Sample 11</b></span>

```{r}
# to change back to original directory
setwd(initial.dir)
```

***Interpretation***:

- change back to the directory path which initial.dir object holds.

\

##### <span style="color:#7b9a26"> <b> Code Sample 12</b></span>

```{r}
# load the iris data from UCI machine learning repo (internet archive)
iris <- read.csv(url('https://archive.ics.uci.edu/ml/machine-learning-databases/iris/iris.data'),header=FALSE)
```

***Interpretation***:

- fetch the data from online repo using url then convert the obtained into dataframe from it.
- `header = FALSE` will not set the header for dataframe. Often done when we want to explicitly define column names ourselves

\

##### <span style="color:#7b9a26"> <b> Code Sample 13</b></span>

```{r}
# look first few values of data
head(iris)
```

***Interpretation***:

- fetch the first few records from the iris dataframe
- since in previous line of code we did `header = FALSE` our column name is defined as V1, V2, V3, V4, V5.

\

##### <span style="color:#7b9a26"> <b> Code Sample 14</b></span>
```{r}
# add column names for V1, V2, V3, V4, V5 columns to iris dataframe
names(iris) <- c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species")
```

***Interpretation***:

- set the name of columns in the iris dataframe `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`, and `Species`

\

##### <span style="color:#7b9a26"> <b> Code Sample 15</b></span>
```{r}
# saving the downloaded file to csv in local system
# write.csv(dataframe_name, "path\file_name.csv", row.names=FALSE)
write.csv(iris,'iris.csv')
```

***Interpretation***:

- writes the csv file in the current working directory as `iris.csv` from iris dataframe
- Also we can set the to another path like this `write.csv(dataframe_name,filepath)
- for example: `write.csv(iris,'C:/Users/SumanPaudel/Desktop/suman.csv')`

\


##### <span style="color:#7b9a26"> <b> Code Sample 16</b></span>
```{r}
# check working directory using
getwd()
```

***Interpretation***:

- returns the current working directory in the console.

\

##### <span style="color:#7b9a26"> <b> Code Sample 17</b></span>
```{r}
# Using forward pipe operator/s in R
# for using pipes in R we need magrittr library
# Hotkey for pipe i.e. is Ctrl + Shift + M in windows and for MacOS CMD + Shift + M
library(magrittr)
iris$Sepal.Length.SQRT <- iris$Sepal.Length %>% sqrt()
```

***Interpretation***:

- computes the square root of `iris$Sepal.Length` and assign it to the new variable `iris$Sepal.Length.SQRT`
- forward pip are very helpful when forwarding and object into function or call the expression

\

##### <span style="color:#7b9a26"> <b> Code Sample 18</b></span>
```{r}
# The assignment pipe, %<>%, is used to update a value by first piping it into one or more rhs expressions,  and then assigning the result.
iris$Sepal.Length %<>% sqrt
```

***Interpretation***:

- computes the square root of `iris$Sepal.Length` and assign computed value to itself.
- while using assignment pipe `%<>%`, we must be careful as original data will be lost.

\

##### <span style="color:#7b9a26"> <b> Code Sample 19</b></span>
```{r}
# random seed
set.seed(123)
```

***Interpretation***:

- sets random seed to generate random number that can be reproduced
- widely used when dealing with classification problems in machine learning

\

##### <span style="color:#7b9a26"> <b> Code Sample 20</b></span>
```{r error=TRUE}
# rnorm generated the random value from normal distribution
rnorm(200) %>% 
  matrix(ncol = 2) %>% 
  plot %>% 
  colSums
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#7b9a26"> <b> Code Sample 21</b></span>
```{r}
# rnorm generated the random value from normal distribution
rnorm(200) %>% 
  matrix(ncol = 2) %T>% 
  plot %>% 
  colSums
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#7b9a26"> <b> Code Sample 22</b></span>
```{r}
# The exposing pipe operator “%$%”
iris %>% 
  subset(Sepal.Length > mean(Sepal.Length)) %$% 
  cor(Sepal.Length, Sepal.Width)
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#7b9a26"> <b> Code Sample 23</b></span>
```{r}
# The exposing pipe operator “%$%”
cor(iris$Sepal.Length, iris$Sepal.Width)
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

### When Not to Use the Pipe

The pipe (`%>%`) is a powerful tool in R, but it's not always the best choice for every situation. Here are some scenarios where we might want to consider alternative approaches:

-   If pipes involves more than ten steps, consider breaking it down into smaller chunks with meaningful intermediate objects. This makes debugging easier and improves code readability.

-   Pipes work best when transforming a single primary object. If you're dealing with multiple inputs or combining several outputs, the pipe may not be the most suitable tool.

-   When your code starts resembling a directed graph with intricate dependencies, using pipes can lead to confusing and convoluted code.
-   When developing internal packages pipe might not be the best go to tool.

### Final Notes

- `%>%` are used widely in R
- `%<>%` used when assignment of variables are required
- `%T%` and `%$%` used when required explicitly on rare occasion. 

\

## <span style="color:#d30000"> <b> Code Execution and Output/Interpretation of Session 5</b></span>

\

##### **Naming Convention In R**

lllowercase
- `adjustcolor` \
period.separated
- `plot.new`  
underscore_separated
- `numeric_version` \
lowerCamelCase
- `addTaskCallback` \
UpperCamelCase
- `SignatureMethod` 

The link https://www.r-bloggers.com/2014/07/consistent-naming-conventions-in-r/ suggest to use underscore sperated variable name as it provides better readbility of code.

\

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   `round(3.14)` rounds the value 3.14.
-   `round(3.14, digits = 2)` to nearest 2 digits.

\

```{r}
# factorial of 3
factorial(3)
# factorial of 3*2
factorial(2*3)
```

***Interpretation***:

-   `factorial(3)` gives the factorial of 3 which is 6.
-   `factorial(3)` gives the factorial of `2*3` which is 720.    

\

##### <span style="color:#7b9a26"> <b> Code Sample 2</b></span>

```{r}
# mean of sequence 1:6
mean(1:6)
# mean of vector 1 to 30
mean(c(1:30))
```

***Interpretation***:

-   `mean(1:6)` computes the mean of sequenec 1:6
-   `mean(c(1:6)` computes the mean of vector 1:30

\

##### <span style="color:#7b9a26"> <b> Code Sample 3</b></span>

```{r}
# random sampling without and with replacement in R using sample function
# sample size 1 without replacement
die <- 1:6
sample(x = die, size = 1)
# sample size 1 without replacement
sample(x = die, size = 1)
# sample size 1 with replacement
sample(x = die, size = 1, replace = TRUE)
```

***Interpretation***:

-   `sample(x = die, size = 1)` samples the size of 1 from die without replacement. without replacement means each element can only be selected once. 
-   `sample(x = die, size = 1, replace = TRUE)` samples the size of 1 from die with replacement. with replacement means elements can be selected more than once.

\

```{r}
# sample size 2 without replacement
sample(x = die, size = 2)
# sample size 2 without replacement
sample(x = die, size = 2)
# sample size 2 with replacement
sample(x = die, size = 2, replace = TRUE)
```

***Interpretation***:

-   `sample(x = die, size = 2)` samples the size of 2 from die without replacement. without replacement means each element can only be selected once.
-   `sample(x = die, size = 2, replace = TRUE)` samples the size of 2 from die with replacement. with replacement means elements can be selected more than once.

\

##### <span style="color:#7b9a26"> <b> Code Sample 4</b></span>

```{r}
# load the iris dataset from current working directory
iris <- read.csv('iris.csv')
set.seed(123)
```

***Interpretation***:

-   `iris <- read.csv('iris.csv')` load the iris dataset from current working directory to iris object.
-   `set.seed(123)` generates the random number which can be reproduced again.

\

##### <span style="color:#7b9a26"> <b> Code Sample 5</b></span>

```{r}
# training testing sample
tt.sample <- sample(c(TRUE, FALSE), nrow(iris), replace=T, prob=c(0.7,0.3))
train <- iris[tt.sample,]
test <- iris[!tt.sample,]
```

***Interpretation***:

-   `tt.sample <- sample(c(TRUE, FALSE), nrow(iris), replace=T)` samples the value given TRUE or FALSE for FALSE number of rows on iris dataset with replacement also with probability weights 0.7 for TRUE and 0.3 for FALSE and store to tt.sample variable.
-   train holds traning sample that are subsetted values from tt.sample in iris dataset. Rows corresponding to TRUE in tt.sample are selected 
-   test holds test sample that are subsetted values which are not TRUE for training set. Rows corresponding to not TRUE in tt.sample are selected
- `!` alters the outcome like `TRUE` becomes `FALSE`.

\

##### <span style="color:#7b9a26"> <b> Code Sample 6</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 7</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 8</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 9</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 10</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 11</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 12</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 13</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 14</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 15</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 16</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 17</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 18</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 19</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#7b9a26"> <b> Code Sample 20</b></span>

```{r}
# column vector 
round(3.14)
round(3.14, digits = 2)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\


