---
title: '**Assignment 2: Web scrapping/Data Wrangling in R**'
author: '**Suman Paudel 33**'
date: "2024-03-03"
output:
  html_document:
    highlight: textmate
  pdf_document: 
    highlight: pygments
  github_document: default
  html_notebook: default
---
[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

## <span style="color:#d30000"> <b> Code Execution and Output/Interpretation of Session 7</b></span>



#### What is a “package” in R?

- In R, the fundamental unit of shareable code/function is the package. 
- A package bundles together code, data, documentation, and tests, and is easy to share with others. 
- The public clearing house for R packages is the Comprehensive R Archive Network or `CRAN`. The details about the packages can be found at CRAN.


#### How to install, use and get help about any package from CRAN?

- We can install packages of CRAN in R using:
**``install.packages("packagename")``**  
For example: **``install.packages("dplyr")``**  

- We can then use the installed packages in R using:  
**``library(packagename) ``**  
**``e.g. library(dplyr)``**  

- We can get help on the installed packages in R using:  
**``?packagement``** or **``help(package = "packagement")``**  
**``e.g. ?dplyr``** OR **``help(package = "dplyr")``**   

#### How to develop a package in R?
https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/

- Step 0: Packages you will need
- Step 1: Creating your package directory
- Step 2: Add functions
- Step 3: Add documentation
- Step 4: Process your documentation
- Step 5: Install
- Step 6: Make a package GitHub repo (Bonus!)
- Step 7: Infinity- Iterate

#### Reading (Import) data in R/R Studio:

- Text files: R base, readr etc
- Excel files: readXL, openxls etc. 
- SPSS, Stata, SAS files: foreign, haven etc. 

#### Reading data in R/R Studio

- JSON files: rjason, jsonlite, RJSONIO etc.

#### To install the library to work on josn files.
```{r eval=FALSE}
# install rjson package to work with json file.
install.packages('rjson')
```

#### Read the created JSON file (json_file.json) in R and Convert it as data.frame for further manipulation in R.

```{r}

library("rjson")
data <- fromJSON(file = "jason_data.json")
# jason_data.json must be in the current working directory of R
print(data)
# covert to data frame:
jason_data_frame <- as.data.frame(data)
print(jason_data_frame) 
```
##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# summary of data
summary(jason_data_frame)

# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <-  as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)

# average salary by department
aggregate(Salary ~ Dept, data = jason_data_frame, FUN = max)

# also using dplyr package
library(dplyr)
library(magrittr)
avg_by_dept <-
  jason_data_frame %>% group_by(Dept) %>% summarise(avg_salart = mean(Salary))

# frequency distribution of all variables
# since tables only shows the frequency distribution of factors, table on numerical or integer value is bad practice.
table(jason_data_frame$Dept)
```

#### Reading data in R/R Studio: Web Scrapping
- HTML page: `rvest` package (from R Studio)
- Use **`rvest`** package to extract HTML tables.

#### Reading JSON file from URL: Web API
- `install.packages('jsonlite')`
- `library('jsonlite')`

# Reading JSON file from URL: Web API 

```{r rows.print=5}
library(jsonlite)

raw <-
  fromJSON((
    "https://data.ny.gov/api/views/9a8c-vfzj/rows.json?accessType=DOWNLOAD"
  ))

food_market <- raw[['data']] 
str(food_market) 
head(food_market)
```

```{r eval=FALSE}
names <- food_market[,14]
head(names)
table(names)
```

```{r error=TRUE}
table(v19)
```

```{r error=TRUE, rows.print=5}

print(table(food_market$V19))
table(food_market[,19])
```


```{r}
# Web scrapping in R: A Simple (barebones) Example
# https://www.dataquest.io/blog/web-scraping-in-r-rvest

# The recommended package for web scrapping in R is “rvest
# using html
library(rvest)
simple <- read_html('https://dataquestio.github.io/web-scraping-pages/simple.html')

simple %>% html_nodes('p') %>% html_text()
```


```{r error=TRUE}
# wikipedia nepal covid 19 
wiki_link <- "https://en.wikipedia.org/wiki/COVID-19_pandemic_in_Nepal"
wiki_page <- read_html(wiki_link)
str(wiki_page)

wiki_page %>% html_nodes("table")

covid_table <- wiki_page %>% html_elements('.COVID-19_pandemic_data_Nepal_medical_cases') %>% html_node('table') %>% html_table()
covid_table <- covid_table[[1]]



names(covid_table) <- paste(names(covid_table), covid_table[1,], sep = "_")
names(covid_table)
covid_table <- covid_table[-1,]

str(covid_table)

colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)

# another way to do same thing 

names(covid_table)[names(covid_table)=='Date_Date'] = 'Date'
names(covid_table)[names(covid_table)=='Confirmed cases_Total'] = 'Confirmed_Cases_Total'
names(covid_table)[names(covid_table)=='Confirmed cases_New'] = 'Confirmed_Cases_New'
names(covid_table)[names(covid_table)=='Confirmed cases_Active'] = 'Confirmed_Cases_Active'
names(covid_table)[names(covid_table)=='Recoveries_Total'] = 'Recoveries_Total'
names(covid_table)[names(covid_table)=='Recoveries_New'] = 'Recoveries_New'
names(covid_table)[names(covid_table)=='Deaths_Total'] = 'Deaths_Total'
names(covid_table)[names(covid_table)=='Deaths_New'] = 'Deaths_New'
names(covid_table)[names(covid_table)=='RT-PCR tests_Total'] = 'PCR_Total'
names(covid_table)[names(covid_table)=='RT-PCR tests_New'] = 'PCR_New'
names(covid_table)[names(covid_table)=='TPR_TPR'] = 'TPR'
names(covid_table)[names(covid_table)=='RR_RR'] = 'RR'
names(covid_table)[names(covid_table)=='CFR_CFR'] = 'CFR'
names(covid_table)[names(covid_table)=='Ref._Ref.'] = 'Ref'


# data wrangling part iii

# removing "+" and "%" from the variables

covid_table$TPR <- gsub('[%]', '', covid_table$TPR)
covid_table$RR <- gsub('[%]', '', covid_table$RR)
covid_table$CFR <- gsub('[%]', '', covid_table$CFR)

# converting  chr variables as 1

covid_table$Confirmed_Cases_Total <-
  as.integer(covid_table$Confirmed_Cases_Total)
covid_table$Confirmed_Cases_New <-
  as.integer(covid_table$Confirmed_Cases_New)
covid_table$Confirmed_Cases_Active <-
  as.integer(covid_table$Confirmed_Cases_Active)
covid_table$Recoveries_Total <-
  as.integer(covid_table$Recoveries_Total)
covid_table$Recoveries_New <-
  as.integer(covid_table$Recoveries_New)

# converting chr variable as integer

covid_table$Deaths_Total <- as.integer(covid_table$Deaths_Total)
covid_table$Deaths_New <- as.integer(covid_table$Deaths_New)
covid_table$PCR_Total <- as.integer(covid_table$PCR_Total)
covid_table$PCR_New <- as.integer(covid_table$PCR_New)

#Data wrangling: Part IV
#Converting “chr” variables as numbers 
covid_table$TPR <- as.numeric(covid_table$TPR)
covid_table$RR <- as.numeric(covid_table$RR)
covid_table$CFR <- as.numeric(covid_table$CFR)


start_date_2020 <- '2020-01-23'
end_date_2020 <- '2020-12-31'
final <- ifelse(1:nrow(covid_table) <= diff, 2020, 2021)
# using base R date time functions
diff <- as.numeric(difftime(end_date_2020,start_date_2020,units = 'days')) + 1
formatted_date <- as.Date(covid_table$Date,format = "%d %b")
formatted_date <- format(formatted_date, '-%m-%d')
final_converted_date <- paste0(final,formatted_date)
class(final_converted_date)

# using lubridate
library(lubridate)
diff <- (ymd(start) %--% ymd(end)) %/% days(1) + 1
final <- ifelse(1:nrow(covid_table) <= diff, 2020, 2021)
formatted_date <- ymd(as.Date(covid_table$Date,format = "%d %b"))
final_converted_date <- make_date(year = final,month = month(formatted_date), day = day(formatted_date))
class(final_converted_date)

```


 