---
title: '**Assignment 2: Web scrapping/Data Wrangling in R**'
author: '**Suman Paudel 33**'
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
  pdf_document: 
    highlight: pygments
---

[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

### [ <b> Code Execution and Output/Interpretation of Session 7</b>]{style="color:#d30000"}

#### What is a “package” in R?

-   In R, the fundamental unit of shareable code/function is the package.
-   A package bundles together code, data, documentation, and tests, and is easy to share with others.
-   The public clearing house for R packages is the Comprehensive R Archive Network or `CRAN`. The details about the packages can be found at CRAN.

#### How to install, use and get help about any package from CRAN?

-   We can install packages of CRAN in R using: **`install.packages("packagename")`**\
    For example: **`install.packages("dplyr")`**

-   We can then use the installed packages in R using:\
    **`library(packagename)`**\
    **`e.g. library(dplyr)`**

-   We can get help on the installed packages in R using:\
    **`?packagement`** or **`help(package = "packagement")`**\
    **`e.g. ?dplyr`** OR **`help(package = "dplyr")`**

#### How to develop a package in R?  

\ <https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/>

-   Step 0: Packages you will need
-   Step 1: Creating your package directory
-   Step 2: Add functions
-   Step 3: Add documentation
-   Step 4: Process your documentation
-   Step 5: Install
-   Step 6: Make a package GitHub repo (Bonus!)
-   Step 7: Infinity- Iterate

#### Reading (Import) data in R/R Studio:

-   Text files: R base, readr etc
-   Excel files: readXL, openxls etc.
-   SPSS, Stata, SAS files: foreign, haven etc.

#### Reading data in R/R Studio

-   JSON files: rjason, jsonlite, RJSONIO etc.

#### To install the library to work on josn files.
-   `install.packages('jsonlite')`
-   `install.packages('rjson')`

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# vector 
library("rjson")
data <- fromJSON(file = "jason_data.json")
data
```

***Interpretation***:

-   loaded the jason_data.json file fromm current working directory using rjson library

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
library("rjson")
data <- fromJSON(file = "jason_data.json")
data
```

***Interpretation***:

-   loaded the jason_data.json file fromm current working directory using rjson library

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# covert to data frame:
jason_data_frame <- as.data.frame(data)
jason_data_frame
```

***Interpretation***:

-   converted the loaded json data into data.frame

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# summary of jason_data_frame
summary(jason_data_frame)
```

***Interpretation***:

-   summarizes the json data frame.

##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <- as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
# average salary by department
aggregate(Salary ~ Dept, data = jason_data_frame, FUN = mean)
```

***Interpretation***:

- aggregates the average salary by department.

```{r}
# also using dplyr package
library(dplyr)
library(magrittr)
avg_by_dept <-
  jason_data_frame %>%
  group_by(Dept) %>%
  summarise(avg_salart = mean(Salary))
```

***Interpretation***:

- average salary by department can be achieved by using dplyr package and using summarise.

```{r}
# frequency distribution of all variables
# since tables only shows the frequency distribution of factors, table on numerical or integer value is bad practice.
table(jason_data_frame$Dept)
```

***Interpretation***:

- since tables only shows the frequency distribution of factors, table on numerical or integer value is bad practice.


#### Reading JSON file from URL: Web API 

```{r cache=TRUE}
# fetch the data from web api
library(jsonlite)
raw <-
  fromJSON(
    "https://data.ny.gov/api/views/9a8c-vfzj/rows.json?accessType=DOWNLOAD")
food_market <- raw[['data']] 
```

***Interpretation***:

- read the json data from API using jsonlite library
- the raw object gets the list of values from where data part is extracted and assigned to food_market object

```{r}
# structure and head of food market
str(food_market) 
head(food_market, n = 4)
```

***Interpretation***:

- returns the structure and head of food_market.

```{r}
names <- food_market[,14]
```

***Interpretation***:

- returns the names stores listed in index 14 of food_market in names object

```{r}
head(names)
head(table(names), n = 7)
```

***Interpretation***:

- `head(names)` returns first few data.
- `head(table(names), n = 7)` returns the frequency table of names of stores.
- since data is so much I restricted to first 7 values for frequency table.

```{r error=TRUE}
table(v19)
```

***Interpretation***:

- trying to get the frequency tabke v19. but v19 doesn't exist and throws error

```{r error=TRUE}
table(food_market$V19)
```

***Interpretation***:

- An atomic vector is a one-dimensional data object created using functions like c() or vector() in R.
- The $ operator is commonly used to access elements of a data frame by column name.
- since food_market is of atomic vectors type, while access the element using $ returned this error.
- this can be mitigated by using `table(food_market[,19])`

```{r, warning=FALSE}
head(table(food_market[, 19]), n = 5)
```

***Interpretation***:

- returns the frequency table of data that is at 19th column of food_market
- since data is too much, I restricted the display to 5.

#### Web scrapping in R: A Simple (barebones) Example

```{r warning=FALSE}
# The recommended package for web scrapping in R is “rvest
# using html
library(rvest)
simple <-
  read_html('https://dataquestio.github.io/web-scraping-pages/simple.html')
simple %>% html_nodes('p') %>% html_text()
```

***Interpretation***:

- reads the html using `read_html()`
- we loaded the html in simple object then using pipes parsed the html with node 'p' then converted that to normal text.

```{r}
# Wikipedia Nepal Covid 19 
wiki_link <- "https://en.wikipedia.org/wiki/COVID-19_pandemic_in_Nepal"
wiki_page <- read_html(wiki_link)
```

***Interpretation***:

- since salary was of character so hist was not produced, so I converted it to integer.
- generates histogram of salary of jason data frame

```{r}
str(wiki_page)
```

***Interpretation***:

- structure of wiki page, returns list of 2 xml node and xml doc

```{r}
wiki_page %>% html_nodes("table")
```

***Interpretation***:

- parses the html nodes containing `table` in html page of wiki_page.

```{r}
covid_table <-
  wiki_page %>% html_elements('.COVID-19_pandemic_data_Nepal_medical_cases') %>% html_node('table') %>% html_table()
covid_table <- covid_table[[1]]
```

***Interpretation***:

- from wiki page, first parsed the html elements having `.COVID-19_pandemic_data_Nepal_medical_cases`
- then extracted the node containing `table` into html_table()
- since the data was returned in the list, the actual data was at first index which is dataframe.


#### Data wrangling: Part I Column names of covid_table
```{r}
names(covid_table) <-
  paste(names(covid_table), covid_table[1, ], sep = "_")
covid_table <- covid_table[-1, ]
names(covid_table)
```

***Interpretation***:

- even though the data was extracted to dataframe there was error in columns and we want to rename it
- concatenated the column names with first row of dataframe.
- and finally dropping the first column.


```{r}
#Check the structure of data again
str(covid_table)
```

***Interpretation***:

- checking the structure again to ensure.

#### Data wrangling: Part II Renaming the column names
- Change “Date_Date” variable as “Date”
- Change “Confirmed cases_Total” variable as “Confirmed_Cases_Total”
- Change “Confirmed cases_New” variable as “Confirmed_Cases_New”
- Change “Confirmed cases_Active” variable as “Confirmed_Cases_Active”
- Change “RT-PCR tests_Total” variable as “RT-PCR_tests_Total”
- Change “RT-PCR tests_New” variable as “RT-PCR_tests_New”
- Change “TPR_TPR” variable as “TPR”
- Change “RR_RR” variable as “RR”
- Change “CFR_CFR” variable as “CFR”
- Change “Ref. _Ref.” variable as “Ref”


```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.


```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r eval=FALSE}
# another way to do same thing 

names(covid_table)[names(covid_table)=='Date_Date'] = 'Date'
names(covid_table)[names(covid_table)=='Confirmed cases_Total'] = 'Confirmed_Cases_Total'
names(covid_table)[names(covid_table)=='Confirmed cases_New'] = 'Confirmed_Cases_New'
names(covid_table)[names(covid_table)=='Confirmed cases_Active'] = 'Confirmed_Cases_Active'
names(covid_table)[names(covid_table)=='Recoveries_Total'] = 'Recoveries_Total'
names(covid_table)[names(covid_table)=='Recoveries_New'] = 'Recoveries_New'
names(covid_table)[names(covid_table)=='Deaths_Total'] = 'Deaths_Total'
names(covid_table)[names(covid_table)=='Deaths_New'] = 'Deaths_New'
names(covid_table)[names(covid_table)=='RT-PCR tests_Total'] = 'PCR_Total'
names(covid_table)[names(covid_table)=='RT-PCR tests_New'] = 'PCR_New'
names(covid_table)[names(covid_table)=='TPR_TPR'] = 'TPR'
names(covid_table)[names(covid_table)=='RR_RR'] = 'RR'
names(covid_table)[names(covid_table)=='CFR_CFR'] = 'CFR'
names(covid_table)[names(covid_table)=='Ref._Ref.'] = 'Ref'
```

***Interpretation***:

- Another way to rename the column names to desired column names.

#### Data Wrangling Part III
```{r}

# removing "+" and "%" from the variables
covid_table$Confirmed_Cases_New <- gsub('[+]', '', covid_table$Confirmed_Cases_New)
covid_table$Recoveries_New <- gsub('[+]', '', covid_table$Recoveries_New)
covid_table$Deaths_New <- gsub('[+]', '', covid_table$Deaths_New)
covid_table$PCR_New <- gsub('[+]', '', covid_table$PCR_New)

covid_table$TPR <- gsub('[%]', '', covid_table$TPR)
covid_table$RR <- gsub('[%]', '', covid_table$RR)
covid_table$CFR <- gsub('[%]', '', covid_table$CFR)

```

***Interpretation***:

- cleaning the messy data using gsub.
- removing `%` and `+` from data.

```{r}
# since in pdf while converting chr to numeric or integer type coerce warning was given for invalid type.
covid_table$Confirmed_Cases_Total <- gsub('[,]', '', covid_table$Confirmed_Cases_Total)
covid_table$Confirmed_Cases_New <- gsub('[,]', '', covid_table$Confirmed_Cases_New)
covid_table$Confirmed_Cases_Active <- gsub('[,]', '', covid_table$Confirmed_Cases_Active)
covid_table$Recoveries_Total <- gsub('[,]', '', covid_table$Recoveries_Total)
covid_table$Recoveries_New <- gsub('[,]', '', covid_table$Recoveries_New)

covid_table$Deaths_Total <- gsub('[,]', '', covid_table$Deaths_Total)
covid_table$Deaths_New <- gsub('[,]', '', covid_table$Deaths_New)
covid_table$PCR_Total <- gsub('[,]', '', covid_table$PCR_Total)
covid_table$PCR_New <- gsub('[,]', '', covid_table$PCR_New)

covid_table$TPR <- gsub('[,]', '', covid_table$TPR)
covid_table$RR <- gsub('[,]', '', covid_table$RR)
covid_table$CFR <- gsub('[,]', '', covid_table$CFR)
```

***Interpretation***:

- Since while converting chr to integer type it gave some warning about coerce where values were invalid type for e.g `313,333` can't be interpreted as integer because of comma. But it is right in context of html in website. 
- removed the `,` using gsub.

#### Data wrangling: Part IV Converting “chr” variables as numbers 

```{r}

covid_table$Confirmed_Cases_Total <-
  as.integer(covid_table$Confirmed_Cases_Total)
covid_table$Confirmed_Cases_New <-
  as.integer(covid_table$Confirmed_Cases_New)
covid_table$Confirmed_Cases_Active <-
  as.integer(covid_table$Confirmed_Cases_Active)
covid_table$Recoveries_Total <-
  as.integer(covid_table$Recoveries_Total)
covid_table$Recoveries_New <-
  as.integer(covid_table$Recoveries_New)

covid_table$Deaths_Total <- as.integer(covid_table$Deaths_Total)
covid_table$Deaths_New <- as.integer(covid_table$Deaths_New)
covid_table$PCR_Total <- as.integer(covid_table$PCR_Total)
covid_table$PCR_New <- as.integer(covid_table$PCR_New)

covid_table$TPR <- as.numeric(covid_table$TPR)
covid_table$RR <- as.numeric(covid_table$RR)
covid_table$CFR <- as.numeric(covid_table$CFR)
```

***Interpretation***:

- converted all of the required columns of chr type of integer or numeric type using `as.numeric()` function.

```{r}
str(covid_table)
```

***Interpretation***:

- finally check the data type.


##### Converting Date (Assignment)
```{r}
head(as.Date(covid_table$Date, format = "%d %b"), n = 50)
```

***Interpretation***:

- By default tries to check this format `"%Y-%m-%d"` or `"%Y/%m/%d"`for given date or string data.
- since out date column has day and month I have to use `%d` for day and `%b` for short name of month.
- returns the value in 2024 but that date is of 2020 and 2021
- In order to work around this I have made a logic below.

```{r }
# using base R date time functions

start_date_2020 <- "2020-01-23"
end_date_2020 <- "2020-12-31"

# check days diff
days_diff <-
  as.numeric(difftime(end_date_2020, start_date_2020, units = 'days')) + 1

# check difference till first n rows and insert value if condition is true return 2020 else 2021
check_year <- ifelse(1:nrow(covid_table) <= days_diff, 2020, 2021)

# format the date according to need
formatted_date <- as.Date(covid_table$Date, format = "%d %b")
formatted_date <- format(formatted_date, '-%m-%d')

# concantante the year and formated day and date
final_converted_date <- paste0(check_year, formatted_date)

# finally since concatenation returns string again convert the type into Date and load the Date column of covid table
covid_table$Date <- as.Date(final_converted_date)
head(covid_table$Date)
class(covid_table$Date)
```

***Interpretation***:

- Since I know that data is of 23rd Jan 2020 to 31st May 2021.
- Also, after 31st Dec next year will arrive, so I set variable `start_date_2020 <- "2020-01-23"` and `end_date_2020 <- "2020-12-31"`.
- I calculated the difference in day from 23rd Jan to 31st Dec.
- Also data is serial in dataframe I filtered the data to 2020 and 2021 using difference in rows. Set `2020` to first 344 rows and rest `2021`.
- since `as.Date(covid_table$Date, format = "%d %b")` gave the date of 2024, I formatted the date and only got day and month.
- Finally concatenated the calulcated year with formatted day and month. 

```{r, warning=FALSE, message=FALSE}
# using lubridate
library(lubridate)

start_date_2020 <- "2020-01-23"
end_date_2020 <- "2020-12-31"

# find difference
diff <-
  (ymd(start_date_2020) %--% ymd(end_date_2020)) %/% days(1) + 1

# check difference till first n rows and insert value if condition is true return 2020 else 2021
check_year <- ifelse(1:nrow(covid_table) <= diff, 2020, 2021)

# format the date to day and month 
formatted_date <- ymd(as.Date(covid_table$Date, format = "%d %b"))

# create the date using make_date function
final_converted_date <-
  make_date(
    year = check_year,
    month = month(formatted_date),
    day = day(formatted_date)
  )
# change the Date column value with final converted date 
covid_table$Date <- final_converted_date
class(covid_table$Date)
```

***Interpretation***:

- Using lubridate to achieve the solution to given problem.



### [ <b> Code Execution and Output/Interpretation of Session 7</b>]{style="color:#d30000"}

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

```{r}
colnames(covid_table) <- c(
  "Date",
  "Confirmed_Cases_Total",
  "Confirmed_Cases_New",
  "Confirmed_Cases_Active",
  "Recoveries_Total",
  "Recoveries_New",
  "Deaths_Total",
  "Deaths_New",
  "PCR_Total",
  "PCR_New",
  "TPR",
  "RR",
  "CFR",
  "Ref"
)
```

***Interpretation***:

- renaming the column names to desired column names.

