---
title: '**Assignment 2: Web scrapping/Data Wrangling in R**'
author: '**Suman Paudel 33**'
date: "2024-03-03"
output:
  html_notebook: default
  pdf_document: 
    highlight: pygments
  github_document: default
  html_document:
    highlight: haddock
---
[GitHub Repository](https://github.com/sumanpaudel1997/R-For-Data-Science/tree/main)

## <span style="color:#d30000"> <b> Code Execution and Output/Interpretation of Session 7</b></span>



#### What is a “package” in R?

- In R, the fundamental unit of shareable code/function is the package. 
- A package bundles together code, data, documentation, and tests, and is easy to share with others. 
- The public clearing house for R packages is the Comprehensive R Archive Network or `CRAN`. The details about the packages can be found at CRAN.


#### How to install, use and get help about any package from CRAN?

- We can install packages of CRAN in R using:
**``install.packages("packagename")``**  
For example: **``install.packages("dplyr")``**  

- We can then use the installed packages in R using:  
**``library(packagename) ``**  
**``e.g. library(dplyr)``**  

- We can get help on the installed packages in R using:  
**``?packagement``** or **``help(package = "packagement")``**  
**``e.g. ?dplyr``** OR **``help(package = "dplyr")``**   

#### How to develop a package in R?
https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/

- Step 0: Packages you will need
- Step 1: Creating your package directory
- Step 2: Add functions
- Step 3: Add documentation
- Step 4: Process your documentation
- Step 5: Install
- Step 6: Make a package GitHub repo (Bonus!)
- Step 7: Infinity- Iterate

#### Reading (Import) data in R/R Studio:

- Text files: R base, readr etc
- Excel files: readXL, openxls etc. 
- SPSS, Stata, SAS files: foreign, haven etc. 

#### Reading data in R/R Studio

- JSON files: rjason, jsonlite, RJSONIO etc.

#### To install the library to work on josn files.
```{r eval=FALSE}
# install rjson package to work with json file.
install.packages('rjson')
```

#### Read the created JSON file (json_file.json) in R and Convert it as data.frame for further manipulation in R.

```{r}

library("rjson")
data <- fromJSON(file = "jason_data.json")
# jason_data.json must be in the current working directory of R
print(data)
# covert to data frame:
jason_data_frame <- as.data.frame(data)
print(jason_data_frame) 
```
##### <span style="color:#7b9a26"> <b> Code Sample 1</b></span>

```{r}
# summary of data
summary(jason_data_frame)

# histogram of salary of jason data frame
# since salary was of character so hist was not produced, so I converted it to integer.
jason_data_frame$Salary <-  as.integer(jason_data_frame$Salary)
hist(jason_data_frame$Salary)
# 
```



 