---
title: "**Project 1: Unit 1**"
author: "**Suman Paudel**"
date: "2024-02-26"
output:
  html_document: default
  pdf_document: default
---

## Code Execution and Output/Interpretation of Session 4


##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# column vector 
x <- c(1:30)
y <- x^3
plot(x,y,)
```

***Interpretation***:

-   x is column vector having elements 1 to 30.\
-   y is also vector having elements of x exponentiated of 3.\
-   plot is a generic function in R to plot, by default scatter plot is plotted.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# store the current working using following command:
initial.dir <- getwd()
initial.dir
```

***Interpretation***:

-   **initial.dir** object will be assigned the current working directory.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# to change the working directory custom directory
setwd("C:/Users/SumanPaudel/Desktop/R For Data Science")
```

***Interpretation***:

-   **setwd()** function will change the working directory to given path.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# loading the necessary packages
library(magrittr)
```

***Interpretation***:

-   In R, the **library()** function will load and attach the required packages.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r eval=FALSE}
# to set the output file and bypass the output of R console and R Studio
sink('session4.out')
```

***Interpretation***:

-   In R, the **sink()** function will set the output file and bypass the output of R console and R Studio.
- until closed, now all the output will be saved in the session4.out file rather than display on.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# load the dataset from the working directory set earlier
iris <- read.csv('iris.csv')
```

***Interpretation***:

- load the iris dataset from csv file using module **read.csv()** function.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r,eval=FALSE}
# plot the iris dataset to do some analysis
plot(iris)
```

***Interpretation***:

- plot a scatter plot from the iris dataset.
- since we have used **sink()** function earlier now the given output will be saved to session4.out

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r,eval=FALSE}
# summary of iris dataset
summary(iris)
```

***Interpretation***:

- In R, **summary** summary is a generic function used to produce result summaries of the results of various model fitting functions.
- since we have used **sink()** function earlier now the given output will be saved to session4.out

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# to close the output file
sink()
```

***Interpretation***:

- Closes the output file that was writing output to it.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# unloading the loaded library
detach("package:magrittr")
```

***Interpretation***:

- Unloads the previous loaded package **magrittr**. 
- Usually use to unload or remove the path of R objects, packages which was attached by using **library()**.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# to change back to original directory
setwd(initial.dir)
```

***Interpretation***:

- change back to the directory path which initial.dir object holds.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# load the iris data from UCI machine learning repo (internet archive)
iris <- read.csv(url('https://archive.ics.uci.edu/ml/machine-learning-databases/iris/iris.data'),header=FALSE)
```

***Interpretation***:

- fetch the data from online repo using url then convert the obtained into dataframe from it.
- `header = FALSE` will not set the header for dataframe. Often done when we want to explicitly define column names ourselves

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>

```{r}
# look first few values of data
head(iris)
```

***Interpretation***:

- fetch the first few records from the iris dataframe
- since in previous line of code we did `header = FALSE` our column name is defined as V1, V2, V3, V4, V5.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# add column names for V1, V2, V3, V4, V5 columns to iris dataframe
names(iris) <- c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species")
```

***Interpretation***:

- set the name of columns in the iris dataframe `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`, and `Species`

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# saving the downloaded file to csv in local system
# write.csv(dataframe_name, "path\file_name.csv", row.names=FALSE)
write.csv(iris,'iris.csv')
```

***Interpretation***:

- writes the csv file in the current working directory as `iris.csv` from iris dataframe
- Also we can set the to another path like this `write.csv(dataframe_name,filepath)
- for example: `write.csv(iris,'C:/Users/SumanPaudel/Desktop/suman.csv')`

\


##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# check working directory using
getwd()
```

***Interpretation***:

- returns the current working directory in the console.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# Using forward pipe operator/s in R
# for using pipes in R we need magrittr library
# Hotkey for pipe i.e. is Ctrl + Shift + M in windows and for MacOS CMD + Shift + M
library(magrittr)
iris$Sepal.Length.SQRT <- iris$Sepal.Length %>% sqrt()
```

***Interpretation***:

- computes the square root of `iris$Sepal.Length` and assign it to the new variable `iris$Sepal.Length.SQRT`
- forward pip are very helpful when forwarding and object into function or call the expression

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# The assignment pipe, %<>%, is used to update a value by first piping it into one or more rhs expressions,  and then assigning the result.
iris$Sepal.Length %<>% sqrt
```

***Interpretation***:

- computes the square root of `iris$Sepal.Length` and assign computed value to itself.
- while using assignment pipe `%<>%`, we must be careful as original data will be lost.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# random seed
set.seed(123)
```

***Interpretation***:

- sets random seed to generate random number that can be reproduced
- widely used when dealing with classification problems in machine learning

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r error=TRUE}
# rnorm generated the random value from normal distribution
rnorm(200) %>% 
  matrix(ncol = 2) %>% 
  plot %>% 
  colSums
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# rnorm generated the random value from normal distribution
rnorm(200) %>% 
  matrix(ncol = 2) %T>% 
  plot %>% 
  colSums
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# The exposing pipe operator “%$%”
iris %>% 
  subset(Sepal.Length > mean(Sepal.Length)) %$% 
  cor(Sepal.Length, Sepal.Width)
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

##### <span style="color:#cc3300"> <b> Code Sample 1</b></span>
```{r}
# The exposing pipe operator “%$%”
cor(iris$Sepal.Length, iris$Sepal.Width)
```

***Interpretation***:

- `rnom(200` generates 200 random number from a normal distribution
- then generated values are converted to matrix with 100 * 2 size.
- then plots the values into scatter plot
- when using `colSums` throws an error because code wont get computed after using plot because it won't return anything except the figure or plot.
- To work around this problem, we can use the “tee” pipe.

\

### When Not to Use the Pipe

The pipe (`%>%`) is a powerful tool in R, but it's not always the best choice for every situation. Here are some scenarios where we might want to consider alternative approaches:

-   If pipes involves more than ten steps, consider breaking it down into smaller chunks with meaningful intermediate objects. This makes debugging easier and improves code readability.

-   Pipes work best when transforming a single primary object. If you're dealing with multiple inputs or combining several outputs, the pipe may not be the most suitable tool.

-   When your code starts resembling a directed graph with intricate dependencies, using pipes can lead to confusing and convoluted code.
-   When developing internal packages pipe might not be the best go to tool.

### Final Notes

- `%>%` are use widely in R
- `%<>%` used when assignment of variables are required
- `%T%` and %$% use when required explicitly on rare occasion. 

\

## Code Execution and Output/Interpretation of Session 5